---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fiinder

<!-- badges: start -->
<!-- badges: end -->

Fiinder allows for simple access to good real estate funds.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
devtools::install_github("92amartins/fiinder")
```
## Usage

At the moment, fiinder is a single-function package. You can use `fiinder::find`
in order to get top brazilian real estate funds in terms of dividend yield and
price.

The most basic usage is to simply call the function with default arguments and
get the results back

```{r usage, message=FALSE}
library(fiinder)
fiinder::find()
```

Alternatively, you can specify the number of funds retrieved (`n`) and other
parameters such as stock liquidity (`liq`) minimum and maximum price/value relations
(`min_p_vpa` and `max_p_vpa` respectively).

```{r}
fiinder::find(n=5, liq = 10000, min_p_vpa = 0.5, max_p_vpa = 1.2)
```
